---
title: "MODIS"
subtitle: "⚔<br/>MODERATE RESOLUTION IMAGING SPECTROMETER"
author: "Sameera Siddiqui"
institute: "RStudio, PBC"
date: "2024/01/21 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader: # output format
    lib_dir: libs #used for dependent libraries 
    nature:
      highlightStyle: tomorrow # how the code displays
      highlightLines: true 
      countIncrementalSlides: false
      #ratio "16:9" # or 4:3
---


# SUMMARY
## What is MODIS ?

*MODIS (or Moderate Resolution Imaging Spectroradiometer) is a key instrument aboard the Terra (originally known as EOS AM-1) and Aqua (originally known as EOS PM-1) satellites. Terra's orbit around the Earth is timed so that it passes from north to south across the equator in the morning, while Aqua passes south to north over the equator in the afternoon. Terra MODIS and Aqua MODIS are viewing the entire Earth's surface every 1 to 2 days, acquiring data in 36 spectral bands, or groups of wavelengths (see MODIS Technical Specifications). 

* MODIS continually collects data in 36 spectral channels with global coverage every 1 to 2 days. 

*Its exceptionally broad spectral range enables MODIS data to be used in studies across numerous disciplines, including vegetative health, changes in land cover and land use, oceans and ocean biology, sea surface temperature, and cloud analysis.

*It also is used extensively for monitoring fires and natural hazards along with oil spills. An important attribute of MODIS data is the availability of MODIS data products in real-time and near real-time. 

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

---
# Writing slides
There are two "types" of slide.

---
class: inverse, center, middle
# Writing slides
There are two "types" of slide.

class: center, middle
# If you don't use inverse you just get a white (or other, depending on your colourscheme) background...



```{r}
remotes::install_github("ropensci/RefManageR")
```
```{r}
library(RefManageR)
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           cite.style = "authoryear",
           style = "markdown",
           hyperlink = TRUE,
           dashed = FALSE,
           no.print.fields=c("doi", "url", "urldate", "issn"))
myBib <- ReadBib("./Bibtex.bib", check = FALSE)
```

```{r}
options(repos = c(CRAN = "https://cran.r-project.org"))
```

```{r}
install.packages("knitcitations")
library(knitcitations)
```
